OpenMPIR

### 2017-10-05 paper.tex
Added acm prelude
Removed minted dependecy

\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\usepackage{minted}
\graphicspath{{./figs/}}

@@

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\settopmatter{printacmref=false}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

@@

To evaluate the use of Tapir we compared performance on the Barcelona OpenMP Task 
Suite to several existing OpenMP implementations. The suite is a set 
of tests intended to test performance of OpenMP implementations
using both irregular and regular tasking.\footnote{An unbalanced tree search benchmark was
very recently added to the suite. Unfortunately we were unable to succesfully run 
it on any implementation, even for medium input sizes. We have therefore left 
it out of our evaluation.  We will continue to work on this benchmark and will 
include the results if the paper is accepted to the workshop.} The following list provides abridged descriptions of 
each benchmark taken verbatim from the test suite distribution.

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\graphicspath{{./figs/}}

@@

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\settopmatter{printacmref=false}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.1145/3148173.3148186}

% ISBN
\acmISBN{978-1-4503-5565-0/17/11}

@@

To evaluate the use of Tapir we compared performance on the Barcelona OpenMP Task 
Suite to several existing OpenMP implementations. The suite is a set of tests
intended to test performance of OpenMP implementations using both irregular and
regular tasking. The following list provides abridged descriptions of each
benchmark taken verbatim from the test suite distribution \cite{bots}.
